State of the Practice for Lattice Boltzmann Method Software

### 2022-01-07 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Updates to LBM SOP

\section{Quantitative Findings and AHP Results} \label{AHPresults}

@@

\begin{table}
	\begin{center}
	\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
	\toprule
	\textbf{Development Tools} & \textbf{Dependencies} & \textbf{Project
	Management Tools} \\
	\midrule
	Continuous Integration & Build Automation Tools & Collaboration Tools\\
	Code Editors & Technical Libraries & Email\\
	Development Environment & Domain Specific Libraries & Change Tracking Tools\\
	Runtime Environments &  & Version Control Tools\\
	Compilers &  & Document Generation Tools\\
	Unit Testing Tools &  & \\
	Correctness Verification Tools &  & \\
	\bottomrule
	\end{tabular}
	\caption{Observed development tools, dependencies and project management
	tools} \label{tbl_tools}
	\end{center}
\end{table}

>>>>

\section{Ranking Projects Based on Quality Measures} \label{AHPresults}

@@

\begin{table}
	\begin{center}
	\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
	\toprule
	\textbf{Development Tools} & \textbf{Dependencies} & \textbf{Project
	Management Tools} \\
	\midrule
	Continuous Integration & Build Automation Tools & Collaboration Tools\\
	Code Editors & Technical Libraries & Email\\
	Development Environments & Domain Specific Libraries & Change Tracking Tools\\
	Runtime Environments &  & Version Control Tools\\
	Compilers &  & Document Generation Tools\\
	Unit Testing Tools &  & \\
	Correctness Verification Tools &  & \\
	\bottomrule
	\end{tabular}
	\caption{Observed development tools, dependencies and project management
	tools} \label{tbl_tools}
	\end{center}
\end{table}
